\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-06-03 paper/ms.tex
Simpler figure

Some illustrative posterior samples are plotted
in Figure~\ref{fig:galaxies}.

\begin{figure}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies.pdf}
\caption{The `galaxy' data, with some illustrative fits drawn
from the posterior distribution.\label{fig:galaxies}}
\end{minipage} \hspace{0.05\textwidth}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies_N.pdf}
\caption{The posterior distribution for $N$ given the
galaxy data.\label{fig:galaxies_N}}
\end{minipage}
\end{figure}

>>>>

The data and the posterior mean fit are shown
in Figure~\ref{fig:galaxies}.

\begin{figure}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies.pdf}
\caption{The `galaxy' data, with the posterior mean fit
(equivalent to the predictive distribution for the ``next'' data point).\label{fig:galaxies}}
\end{minipage} \hspace{0.05\textwidth}
\begin{minipage}{0.45\textwidth}
\centering
\includegraphics[width=0.95\textwidth]{figures/galaxies_N.pdf}
\caption{The posterior distribution for $N$ given the
galaxy data.\label{fig:galaxies_N}}
\end{minipage}
\end{figure}
